Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2014-12-28 Paper/paperN.tex
NIPS style paper

\documentclass[11pt,twocolumn,DIV=11]{scrartcl}

@@

@@

@@

\bibliography{refs.bib}
\end{document}

>>>>

%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}

@@

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\nipsfinalcopy % Uncomment for camera-ready version

@@

\begin{abstract}
The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
The word \textbf{Abstract} must be centered, bold, and in point size 12. Two
line spaces precede the abstract. The abstract must be limited to one
paragraph.
\end{abstract}

@@

\bibliography{refs.bib}

\end{document}
